Taking Dyads Seriously

### 2018-04-12 paper/coverletter/netsMatter_coverLetter.tex
wrappig up; ; git push

\vspace{1.5in}

@@

\vspace{0.5in}

@@

Among political scientists using statistical models to analyze network data there has emerged a dispute between the advocates of the Exponential Random Graph (ERGM) model and those building on the ``latent space'' approach pioneered by Hoff, Raftery, and Handcock. It is worth noting that this fight is not mirrored in the statistical or broader networks literature, as in those communities people recognize these models as having distinct goals.

In political science, however, the dispute has become quite prevalent. Although we clearly work in the latent space world, this paper is not about engaging or extending the ERGM-latent space discussion. Rather, we evaluate the utility of the AME framework using a simulation based exercise and a replication of five recently published works from the field of International Relations. Through the simulation exercise, we show that in the presence of unobserved dependencies the model is able to provide less biased estimates and better calibrated standard errors than extant approaches in the literature. Next, for nearly all of the replications reestimated using the AME framework we find that the case for the key findings from the original works become much less compelling. Additionally, we show through an out-of-sample cross-validation exercise that the AME approach uniformly outperforms each of the replicated approaches in capturing the data generating process of the event of interest.\\[1ex]

We believe that the AME framework is of notable interest to political scientists broadly, and that this study provides not only an introduction but a strong case for its applicability to the questions that we are seeking to address.\\[1ex]

We look forward to your evaluation of this paper.\\[1ex]

>>>>

\vspace{.5in}

@@

\vspace{0.25in}

@@

Among political scientists using statistical models to analyze network data there has emerged a dispute between the advocates of the Exponential Random Graph (ERGM) model and those building on the ``latent space'' approach pioneered by Hoff, Raftery, and Handcock. This fight is not mirrored in the statistical or broader networks literature, as in those communities people recognize these models as having distinct goals. \\[1ex]

In political science, however, the dispute has become quite prevalent. Although we clearly work in the latent space world, this paper is not about engaging or extending the ERGM-latent space discussion. Rather, we evaluate the utility of the AME framework using a simulation based exercise and a replication of three recently published works from the field of International Relations. Through the simulation exercise, we show that in the presence of unobserved dependencies the model is able to provide less biased estimates and better calibrated standard errors than extant approaches in the literature. Next, for nearly all of the replications reestimated using the AME framework we find that the case for the key findings from the original works become much less compelling. Additionally, we show through an out-of-sample cross-validation exercise that the AME approach uniformly outperforms each of the replicated approaches in capturing the data generating process of the event of interest.\\[1ex]

We believe that the AME framework is of notable interest to political scientists broadly, and that this study provides not only an introduction but a strong case for its applicability to the questions that we are seeking to address. We look forward to your evaluation of this paper.\\[1ex]
